SunPy - Python for Solar Physics

### 2014-01-26 4-Util.tex
added short section on Instruments to Util

>>>>

\subsubsection{Instruments}
In addition to providing support for solar data via the main data classes \texttt{Map}, \texttt{LightCurve} and \texttt{Spectrum}, some instrument-specific functions may be found within the \texttt{instr} package. These functions are generally those that are unique to one particular solar instrument, rather than of general use, for example a function to construct a GOES flare event list or a function to query the LYRA timeline annotation file. Currently, functions are included in this way for the GOES, LYRA, RHESSI and IRIS instruments.
